---
title: ""
output: 
  pdf_document:
    latex_engine: pdflatex
header-includes:
  - \usepackage{float}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}  % Clear all header and footer fields
  - \renewcommand{\headrulewidth}{0pt}  % Remove the header rule
  - \renewcommand{\footrulewidth}{0.4pt}  % Add a footer rule
  - \fancyfoot[C]{\small © 2024 Gazar and Calder. All rights reserved. Licensed under the Creative Commons Attribution 4.0 International License.}
geometry: margin=0.75in  # Sets all margins to 0.75 inches
params:
  facility_name: "Facility Name"
  facility_id: "Facility ID"
  unit_id: "Unit ID"
  state: "State"
  county: "County"
  primary_fuel: "Fuel Type"
  emissions_data_facility: NULL
  gen_data: NULL
  npc: NULL
  min_gen: NULL
  mean_gen: NULL
  max_gen: NULL
  emissions_sum: NULL
---


```{r, echo=FALSE, results="asis"}
# Load necessary libraries
library(ggplot2)
library(lubridate)
library(dplyr)
library(tidyr)
library(knitr)

# Set up facility information
facility_name <- params$facility_name
facility_id <- params$facility_id
unit_id <- params$unit_id
state <- params$state
county <- params$county
primary_fuel <- params$primary_fuel
emissions_data_facility <- params$emissions_data_facility
gen_data <- params$gen_data
npc <- params$npc
min_gen <- params$min_gen
mean_gen <- params$mean_gen
max_gen <- params$max_gen
emissions_sum <- params$emissions_sum

# Facility name on the top right
cat(sprintf('
\\begin{flushright}
\\huge{\\textbf{%s, %s}}
\\end{flushright}', facility_name, state))

# Facility details
cat(sprintf('
\\textbf{Facility Information}

Facility ID: \\textbf{%s} \\
Unit ID: \\textbf{%s} \\
State: \\textbf{%s} \\
County: \\textbf{%s} \\
Primary fuel type: \\textbf{%s} \\
Associated generators - nameplate capacity (MW): \\textbf{%s} \\
Historical hourly generation (MWh): \\textbf{%s [%s-%s]}
', facility_id, unit_id, state, county, primary_fuel, npc, mean_gen, min_gen, max_gen))


## Table 1
# Sum the generation and emissions for the relevant percentiles
summary_table <- data.frame(
  Metric = c("Electricity generation (GWh)", "CO2 emissions (thousand tons)", "NOx emissions (thousand lbs)", "SO2 emissions (thousand lbs)", "Heat input (thousand mmBtu)"),
  
  `P01` = round(c(
    sum(emissions_data_facility$Gen_1[is.finite(emissions_data_facility$Gen_1)] / 1e3, na.rm = TRUE),  # Convert MW to GWh
    sum(emissions_data_facility$Gen_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$CO2_1)] * emissions_data_facility$CO2_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$CO2_1)] / 1e3, na.rm = TRUE),  # Convert to thousand tons
    sum(emissions_data_facility$Gen_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$NOx_1)] * emissions_data_facility$NOx_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$NOx_1)] / 1e3, na.rm = TRUE),  # Convert to thousand lbs
    sum(emissions_data_facility$Gen_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$SO2_1)] * emissions_data_facility$SO2_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$SO2_1)] / 1e3, na.rm = TRUE),  # Convert to thousand lbs
    sum(emissions_data_facility$HI_1[is.finite(emissions_data_facility$HI_1)], na.rm = TRUE) / 1e3
  ), 1),
  
  `P25` = round(c(
    sum(emissions_data_facility$Gen_25[is.finite(emissions_data_facility$Gen_25)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$CO2_25)] * emissions_data_facility$CO2_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$CO2_25)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$NOx_25)] * emissions_data_facility$NOx_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$NOx_25)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$SO2_25)] * emissions_data_facility$SO2_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$SO2_25)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$HI_25[is.finite(emissions_data_facility$HI_25)], na.rm = TRUE) / 1e3
  ), 1),
  
  `P50` = round(c(
    sum(emissions_data_facility$Gen_50[is.finite(emissions_data_facility$Gen_50)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$CO2_50)] * emissions_data_facility$CO2_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$CO2_50)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$NOx_50)] * emissions_data_facility$NOx_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$NOx_50)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$SO2_50)] * emissions_data_facility$SO2_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$SO2_50)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$HI_50[is.finite(emissions_data_facility$HI_50)], na.rm = TRUE) / 1e3
  ), 1),
  
  `P75` = round(c(
    sum(emissions_data_facility$Gen_75[is.finite(emissions_data_facility$Gen_75)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$CO2_75)] * emissions_data_facility$CO2_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$CO2_75)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$NOx_75)] * emissions_data_facility$NOx_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$NOx_75)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$SO2_75)] * emissions_data_facility$SO2_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$SO2_75)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$HI_75[is.finite(emissions_data_facility$HI_75)], na.rm = TRUE) / 1e3
  ), 1),
  
  `P99` = round(c(
    sum(emissions_data_facility$Gen_99[is.finite(emissions_data_facility$Gen_99)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$CO2_99)] * emissions_data_facility$CO2_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$CO2_99)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$NOx_99)] * emissions_data_facility$NOx_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$NOx_99)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$Gen_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$SO2_99)] * emissions_data_facility$SO2_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$SO2_99)] / 1e3, na.rm = TRUE),
    sum(emissions_data_facility$HI_99[is.finite(emissions_data_facility$HI_99)], na.rm = TRUE) / 1e3
  ), 1)
)


# Dynamically create the caption with facility name and unit ID
caption_text <- sprintf("Stochastic estimation of annual generation and emissions for %s powerplant, %s (Unit ID: %s)", facility_name, state, unit_id)

# Display the summary table with the dynamically generated caption
kable(summary_table, caption = caption_text, align = "l")

## Table 2
# Sum the generation and emissions for the relevant percentiles
summary_table <- data.frame(
  Metric = c("CO2 emissions (%)", "NOx emissions (%)", "SO2 emissions (%)"),
  
  `P01` = round(c(
    sum(emissions_data_facility$Gen_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$CO2_1)] * emissions_data_facility$CO2_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$CO2_1)] / (10 * emissions_sum$CO2_1), na.rm = TRUE),  # Convert to thousand tons
    sum(emissions_data_facility$Gen_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$NOx_1)] * emissions_data_facility$NOx_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$NOx_1)] / (10 * emissions_sum$NOx_1), na.rm = TRUE),  # Convert to thousand lbs
    sum(emissions_data_facility$Gen_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$SO2_1)] * emissions_data_facility$SO2_1[is.finite(emissions_data_facility$Gen_1) & is.finite(emissions_data_facility$SO2_1)] / (10 * emissions_sum$SO2_1) , na.rm = TRUE)
  ), 1),
  
  `P25` = round(c(
    sum(emissions_data_facility$Gen_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$CO2_25)] * emissions_data_facility$CO2_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$CO2_25)] / (10 * emissions_sum$CO2_25), na.rm = TRUE),
    sum(emissions_data_facility$Gen_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$NOx_25)] * emissions_data_facility$NOx_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$NOx_25)] / (10 * emissions_sum$NOx_25), na.rm = TRUE),
    sum(emissions_data_facility$Gen_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$SO2_25)] * emissions_data_facility$SO2_25[is.finite(emissions_data_facility$Gen_25) & is.finite(emissions_data_facility$SO2_25)] / (10 * emissions_sum$SO2_25), na.rm = TRUE)
  ), 1),
  
  `P50` = round(c(
    sum(emissions_data_facility$Gen_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$CO2_50)] * emissions_data_facility$CO2_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$CO2_50)] / (10 * emissions_sum$CO2_50), na.rm = TRUE),
    sum(emissions_data_facility$Gen_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$NOx_50)] * emissions_data_facility$NOx_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$NOx_50)] / (10 * emissions_sum$NOx_50), na.rm = TRUE),
    sum(emissions_data_facility$Gen_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$SO2_50)] * emissions_data_facility$SO2_50[is.finite(emissions_data_facility$Gen_50) & is.finite(emissions_data_facility$SO2_50)] / (10 * emissions_sum$SO2_50), na.rm = TRUE)
  ), 1),
  
  `P75` = round(c(
    sum(emissions_data_facility$Gen_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$CO2_75)] * emissions_data_facility$CO2_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$CO2_75)] / (10 * emissions_sum$CO2_75), na.rm = TRUE),
    sum(emissions_data_facility$Gen_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$NOx_75)] * emissions_data_facility$NOx_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$NOx_75)] / (10 * emissions_sum$NOx_75), na.rm = TRUE),
    sum(emissions_data_facility$Gen_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$SO2_75)] * emissions_data_facility$SO2_75[is.finite(emissions_data_facility$Gen_75) & is.finite(emissions_data_facility$SO2_75)] / (10 * emissions_sum$SO2_75), na.rm = TRUE)
  ), 1),
  
  `P99` = round(c(
    sum(emissions_data_facility$Gen_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$CO2_99)] * emissions_data_facility$CO2_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$CO2_99)] / (10 * emissions_sum$CO2_99), na.rm = TRUE),
    sum(emissions_data_facility$Gen_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$NOx_99)] * emissions_data_facility$NOx_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$NOx_99)] / (10 * emissions_sum$NOx_99), na.rm = TRUE),
    sum(emissions_data_facility$Gen_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$SO2_99)] * emissions_data_facility$SO2_99[is.finite(emissions_data_facility$Gen_99) & is.finite(emissions_data_facility$SO2_99)] / (10 * emissions_sum$SO2_99), na.rm = TRUE)
  ), 1)
)

# Dynamically create the caption with facility name and unit ID
caption_text <- sprintf("Stochastic estimation of annual emissions for %s powerplant, %s (Unit ID: %s) compared to annual emissions in the state", facility_name, state, unit_id)

# Display the summary table with the dynamically generated caption
kable(summary_table, caption = caption_text, align = "l")

## Plot 1
# Convert DayLabel to Date correctly
emissions_data_facility$Date <- as.Date(emissions_data_facility$DayLabel, format = "%Y-%m-%d")  # Adjust format as needed

# Define Season based on Date
emissions_data_facility$Season <- case_when(
  month(emissions_data_facility$Date) %in% c(12, 1, 2) ~ "Winter",
  month(emissions_data_facility$Date) %in% c(3, 4, 5) ~ "Spring",
  month(emissions_data_facility$Date) %in% c(6, 7, 8) ~ "Summer",
  month(emissions_data_facility$Date) %in% c(9, 10, 11) ~ "Fall",
  TRUE ~ NA_character_
)

# Prepare the data
gen_data <- emissions_data_facility %>%
  select(Hour, Season, Gen_1, Gen_5, Gen_25, Gen_50, Gen_75, Gen_95, Gen_99)

# Ensure that Hour and Season are not missing
gen_data <- gen_data %>% drop_na(Hour, Season)

# Gather the data into long format
gen_long <- gen_data %>%
    pivot_longer(
        cols = starts_with("Gen_"),
        names_to = "Percentile",
        values_to = "Generation"
    ) %>%
    mutate(
        Percentile = as.numeric(sub("Gen_", "", Percentile))
    )


# Filter for the required percentiles
gen_filtered <- gen_long %>%
  filter(Percentile %in% c(1, 5, 25, 50, 75, 95, 99))

# Spread the data to wide format for plotting ribbons
gen_wide <- gen_filtered %>%
    pivot_wider(
        names_from = Percentile,
        values_from = Generation,
        names_prefix = "P",
        values_fn = mean  # Use a summary function to handle duplicates
    )

# Convert 'Hour' to numeric if necessary
gen_wide$Hour <- as.numeric(as.character(gen_wide$Hour))

# Ensure 'Season' is a factor
gen_wide$Season <- factor(gen_wide$Season, levels = c("Winter", "Spring", "Summer", "Fall"))

# Identify the generation columns
gen_cols <- grep("^P", names(gen_wide), value = TRUE)

# Convert generation columns to numeric
gen_wide[gen_cols] <- lapply(gen_wide[gen_cols], function(x) as.numeric(as.character(x)))

# Handle NAs if necessary
gen_wide <- gen_wide %>% drop_na(all_of(gen_cols))

# Create a baseline DayLabel from 1 to 366 (for leap year) and Hour from 1 to 24
daylabel_baseline <- expand.grid(DayLabel = 1:366, Hour = 1:24)

daylabel_baseline$Date <- as.Date(daylabel_baseline$DayLabel, format = "%Y-%m-%d")  # Adjust format as needed

# Define Season based on Date
# Add the 'Season' column
daylabel_baseline$Season <- case_when(
  month(daylabel_baseline$Date) %in% c(12, 1, 2) ~ "Winter",
  month(daylabel_baseline$Date) %in% c(3, 4, 5) ~ "Spring",
  month(daylabel_baseline$Date) %in% c(6, 7, 8) ~ "Summer",
  month(daylabel_baseline$Date) %in% c(9, 10, 11) ~ "Fall",
  TRUE ~ NA_character_
)

# Drop 'DayLabel' and 'Date' columns
daylabel_baseline <- daylabel_baseline[ , !(colnames(daylabel_baseline) %in% c("DayLabel", "Date"))]

# Merge the baseline with your actual generation data (assuming 'DayLabel' and 'Hour' exist in your data)
gen_wide <- merge(daylabel_baseline, gen_wide, by = c("Season", "Hour"), all.x = TRUE)

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.align='center', warning=FALSE, message=FALSE}
# Generate the plot with corrected legend and grey background
ggplot(gen_wide, aes(x = Hour)) +
  # Shaded area between P1 and P99
  geom_ribbon(aes(ymin = P1, ymax = P99, fill = 'P1-P99'), alpha = 0.4) +
  # Shaded area between P5 and P95
  geom_ribbon(aes(ymin = P5, ymax = P95, fill = 'P5-P95'), alpha = 0.6) +
  # Shaded area between P25 and P75
  geom_ribbon(aes(ymin = P25, ymax = P75, fill = 'P25-P75'), alpha = 0.6) +
  # Median line
  geom_line(aes(y = P50, color = 'Median'), size = 1) +
  facet_wrap(~ Season, ncol = 2) +
  labs(
    title = sprintf(
      'Simulated average stochastic hourly electricity generation distribution across seasons \nshowing mean percentile ranges per hour for %s, %s, Unit ID: %s',
      params$facility_name, params$state, params$unit_id
    ),
    x = 'Hour',
    y = 'Generation (MWh)',
    caption = 'Note: This plot only shows hours where EPA CAMD data was available for simulation; \nhours with missing data are not plotted.'
  ) +
  scale_x_continuous(breaks = seq(1, 24, by = 3)) +  # Fewer x-axis ticks
  scale_fill_manual(
    name = NULL,
    values = c('P1-P99' = 'lightblue', 'P5-P95' = 'skyblue', 'P25-P75' = 'blue'),
    labels = c('1st-99th Percentile', '5th-95th Percentile', '25th-75th Percentile'),
    breaks = c('P1-P99', 'P5-P95', 'P25-P75')
  ) +
  scale_color_manual(
    name = NULL,
    values = c('Median' = 'black'),
    labels = c('50th Percentile'),
    breaks = c('Median')
  ) +
  theme_gray() +  # Use the default grey theme
  theme(
    plot.title = element_text(hjust = 0.5, size = 10),  # Decreased title size from 14 to 12
    plot.caption = element_text(hjust = 0.5, size = 8),  # Caption size remains the same
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right",       # Position legend to the right
    legend.direction = "vertical",   # Make legend vertical
    legend.title = element_blank(),  # Remove legend title
    strip.background = element_rect(fill = "grey80"),  # Grey background for facet labels
    strip.text = element_text(color = "black")         # Black text for facet labels
  )

